In this section, the layer is described in terms of the hardware and software design. Specific implementation details, such as hardware components, programming languages, software dependencies, operating systems, etc. should be discussed. Any unnecessary items can be ommitted (for example, a pure software module without any specific hardware should not include a hardware subsection). The organization, titles, and content of the sections below can be modified as necessary for the project.

\subsection{User Interface}
A description of any involved hardware components for the layer. For example, if each subsystem is a software process running on an embedded computer, discuss the specifics of that device here. Do not list a hardware component that only exists at the subsystem level (include it in the following sections).
The website used to control the system will be compatible with major web browsers and will be connected to a database and with the brewing system. Website is verified to work on Chrome for Windows 10, version 91.0.4472.124, and Chrome for MacOS Big Sur, version 91.0.4472.124

\subsection{Layer Operating System}
A description of any operating systems required by the layer.
Website available on Windows 10 version 21H1 and MacOS Big Sur version 11.4

\subsection{Layer Software Dependencies}
A description of any software dependencies (libraries, frameworks, etc) required by the layer.
The user interface components will depend on Mulesoft's Mule software, version 4.3.0

\subsection{Website}
Descibe at a high level the purpose and basic design of this subsystem. Is it a piece of hardware, a class, a web service, or something else? Note that each of the subsystem items below are meant to be specific to that subystem and not a repeat of anything discussed above for the overall layer.
The website provided to the user will have multiple responsabilities. First, it will display real-time information relevant to the user about the current brew. The website will also display a controls section for the user to interact with the brewing system. The information send to and from the website will be sent to the servers and then to the brewing system utilizing the above mentioned Mulesoft software.

\subsubsection{Subsystem Operating System}
A description of any operating systems required by the subsystem.
No specific operating system required.

\subsubsection{Subsystem Software Dependencies}
A description of any software dependencies (libraries, frameworks, design software for mechanical parts or circuits, etc) required by the subsystem.
The website and UI will utilize the React JS library

\subsubsection{Subsystem Programming Languages}
A description of any programming languages used by the subsystem.
JavaScript will be used for creating the website.

\subsubsection{Subsystem Data Structures}
A description of any classes or other data structures that are worth discussing for the subsystem. For example, data being transmitted from a microcontroller to a PC via USB should be first be assembled into packets. What is the structure of the packets?
None

\subsubsection{Subsystem Data Processing}
A description of any algorithms or processing strategies that are worth discussing for the subsystem. If you are implementing a well-known algorithm, list it. If it is something unique to this project, discuss it in greater detail.
None


